Improving the communication and transparency of stock assessment using interactive

### 2018-11-05 manuscript.Rmd
Draft a new second paragraph

The field of stock assessment is no stranger to complex data and models...

A primary role of stock assessment is to provide fisheries managers with the information needed to adequately manage a fishery. Stock assessment involves the use of various sources of data and statistical methods to determine the status of one or more fish stocks and to make quantitative predictions of the consequences of different management choices [@hilborn1992]. A wide array data may be collected for an assessment and, formally, an assessment often reduces to algorithms that convert these data to advice for fisheries managers. In some cases, particularly for commercially valuable species, this means that hundreds or thousands of historical data points from the monitoring program of a stock gets reduced into a single policy value, such as a recommended catch quota [@maunder2009].

@@

Good example from Keith: https://www.nature.com/articles/s41467-018-03297-7

@@

>>>>

The field of fisheries research has a long history of collecting and synthesizing a plethora of data using state-of-the-art computational technologies [@megrey2008]. Fisheries science has evolved alongside the rise of the computing era, and as tools improve so does the management advice provided by fisheries scientists. This management advice generally culminates from a stock assessment process whereby various sources of data and statistical methods are used to model the history, current status and future status of one or more fish stocks [@hilborn1992]. Recent advances in computational technologies have streamlined the process of stock assessment by facilitating the development and application of integrated stock assessment models [@maunder2013]. This means that analyses that were once carried out independently on different data sets can now be integrated into the one analysis by using statistical modeling tools such as JAGS [@plummer2003], AD Model Builder [@fournier2012] and Template Model Builder [@kristensen2015]. From a computational perspective, analyses of a variety of large data sets has never been easier. However, from a human perspective, contemporary stock assessment biologists are faced with the challenge managing data from a variety of sources and also understanding the algorithms that convert these data to advice for fisheries managers.

Note: still not liking the flow between the first and second paragraph. Still seems like I need to cut to the chase sooner...how can interactive visuals help?

A wide array data may be collected for an assessment and, formally, the process often reduces to algorithms that convert these data to advice for fisheries managers. In some cases, particularly for commercially valuable species, this means that hundreds or thousands of historical data points from the monitoring program of a stock gets reduced into a single policy value, such as a recommended catch quota [@maunder2009]. Sound management advice therefore hinges on the ability of stock assessment biologists to manage, interpret and communicate large volumes of data from a variety of sources.

...need to get to the point here quicker...what is the problem and how can interactive visualization tools help?

@@

https://www.nature.com/articles/s41467-018-03297-7

@@

"The ultimate objective of Fisheries Science is to inform management" (http://www.fao.org/tempref/docrep/fao/008/a0212e/a0212E02.pdf)
